\documentclass[a4paper,oneside]{bth}

\usepackage{amsmath}
\usepackage{mathenv}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{textcomp}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{changepage}
\usepackage{listings}
\usepackage{url}
\usepackage{xspace}
\usepackage{xtab}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{subcaption}
\DeclareGraphicsExtensions{.pdf, .png, .jpg}

\newtheorem{lem}{\textsc{Lemma}}[chapter]
\newtheorem{thm}{\textsc{Theorem}}[chapter]
\newtheorem{prop}{\textsc{Proposition}}[chapter]
\newtheorem{post}{Postulate}[chapter]
\newtheorem{corr}{\textsc{Corollary}}[chapter]
\newtheorem{defs}{\textsc{Definition}}[chapter]
\newtheorem{cons}{\textsc{Constraint}}[chapter]
\newtheorem{ex}{\textbf{Example}}[chapter]
\newtheorem{qu}{\textbf{Question}}[chapter]

\newcommand\tab[1][1cm]{\hspace*{#1}} % Add \tab :D



\begin{document}

\pagestyle{plain}
\pagenumbering{roman}


% FRONT MATTER
%-------------
% Please change the data below appropriately.
% The data will be used to generate text in various places on the
% thesis front and inner pages.
%-------------
% The month year when your final report was submitted.
\newcommand{\thesisMonth}{June}
\newcommand{\thesisYear}{2017}

% The degree name you are submitting your thesis for.
% This must be one of the following:
%    Bachelor of Science in Computer Science
%    Bachelor of Science in Digital Game Development
%    Master of Science in Computer Science
%    Master of Science in Software Engineering
%    Master of Science in Telecommunication Systems
\newcommand{\thesisDegree}{Bachelor of Science in Computer Science}

% Course time in weeks. For a 15 credits course this should be 10 and
% for a 30 credits course, this should be 20 weeks.
% Note that the week figure is the same whether you work alone or in a pair.
\newcommand{\thesisWeeks}{10}


% THESIS FRONT PAGE (here you insert title, subtitle and author names)
{\pagestyle{empty}
\changepage{5cm}{1cm}{-0.5cm}{-0.5cm}{}{-2cm}{}{}{}
\noindent
\begin{tabular}{@{}p{0.75\textwidth} p{0.25\textwidth}}
\thesisDegree & \hfill\multirow{3}{*}{\bthcsnotextlogo{3cm}} \\
\thesisMonth \ \thesisYear & \\
\end{tabular}

\begin{center}

\vspace {7.5cm}

% TITLE
{\Huge\textbf{Procedural city generation\\*[0.25cm]using Perlin noise}}

\vspace {0.5cm}

% SUBTITLE (if you have one)
% You should exclude this line, if you don't have a subtitle.
%{\Large\textbf{Thesis Subtitle}}

\vspace {3cm}

% AUTHOR NAMES
% Use the first version for single authors.
% The second version is for two authors on separate rows
%{\Large\textbf{Firstname Lastname}} % first version
{\Large\textbf{Niclas Olsson \\*[0.25cm] Elias Frank}} %second version

\end{center}

\vspace*{\fill}

\noindent%
{\small 
Faculty of Computing \\
Blekinge Institute of Technology \\
SE--371 79 Karlskrona, Sweden
}

\clearpage
} % Back to \pagestyle{plain}


% THESIS INNER PAGE (contact information to authors and supervisors go gere)
{\pagestyle{empty}
\changepage{5cm}{1cm}{-0.5cm}{-0.5cm}{}{-2cm}{}{}{}
\noindent
% Do not change the text below.
{\small
This thesis is submitted to the Faculty of Computing at Blekinge Institute
of Technology in partial fulfillment of the requirements for the degree of
\thesisDegree. The thesis is equivalent to \thesisWeeks\ 
weeks of full time studies.
}

\vspace{15cm}

\noindent
\textbf{Contact Information:} \\
Author(s): \\
Niclas Olsson \\
Elias Frank \\
E-mail:\\
niod12@student.bth.se \\
elfa14@student.bth.se

\vspace{2cm}

\noindent
University advisor: \\
Hans Tap, PhD \\
Department of Creative Technologies


\vspace*{\fill}

\noindent
\begin{tabular}{@{}p{0.5\textwidth} l c l}
Faculty of Computing             & Internet & : & www.bth.se \\
Blekinge Institute of Technology & Phone    & : & +46 455 38 50 00 \\
SE--371 79 Karlskrona, Sweden    & Fax      & : & +46 455 38 50 57 \\
\end{tabular}
\clearpage
} % Back to \pagestyle{plain}

\setcounter{page}{1}

% ABSTRACT PAGE (in \pagestyle{plain})
\abstract
\begin{changemargin}{+.5cm}{+.5cm}
\noindent
\textbf{Context}: Procedural content generation is to algorithmically generate content. This has been used in games and is an important tool to create games with large amounts of content using fewer resources. This may allow small developers to create big worlds, which makes the investigation into this area interesting.\newline
\textbf{Objectives}: The Procedural generation of cities using Perlin noise is explored. The goal is to find out if a procedurally generated city using Perlin noise is viable to use in games. \newline
\textbf{Methods}: An implementation generating cities using Perlin noise has been created and a user study along with data collection tests the cities' viability in games.\newline
\textbf{Results}: The implementation succeeds with all the technical requirements such as performance and determinism. The user study shows that the cities created are perceived as viable in games. \newline
\textbf{Conclusions}. ...

\vspace {1cm}
% You can list 3-4 keywords, maximum 2 of these from the title;
% starts 1 line below the abstract.
\noindent
\textbf{Keywords:} Procedural city generation, Perlin noise, Performance, Game content

\end{changemargin}


% TABLE OF CONTENTS PAGES (generated by LaTeX using the command(s) below)
% You should uncomment the commands you need.
\tableofcontents
%\listoffigures             % in case you have them
%\listoftables              % in case you have them
%\listofalgorithms          % in case you have them
%\include{acknowledgments}  % OPTIONAL

\cleardoublepage
\pagestyle{headings}
\pagenumbering{arabic}


% THE ACTUAL THESIS STARTS HERE
\chapter{Introduction}
\input{introduction}

\chapter{Related work}
\input{related_work}

\chapter{Theoretical framework}
\input{theoretical_framework}

\chapter{Method}
\input{method}

\chapter{Results}
\input{results}

\chapter{Discussion}
\input{discussion}

\chapter{Conclusion and future work}
\input{conclusion}

\bibliography{citations}
\bibliographystyle{plain}
\end{document}
